Type Refinements for the Working Class

### 2015-12-22 paper.tex
wording

>>>>

Our purpose in fixing a semantic universe is emphatically \emph{not} to give a
mathematical interpretation or model of type theory inside set theory, though
it is possible to read our construction in this metamathematical light---however,
the vocabulary of the pretopos $\SemU$ gives us a perspicuous notation in which
to propound what we consider to be an informal (pre-mathematical) meaning
explanation in the sense of Heyting~\cite{heyting:1956} and
Martin-L\"of~\cite{martin-lof:1979}.
\footnote{
  Both Gambino~\cite{gambino:2002} and Dybjer~\cite{dybjer:2012} give lucid
  explanations of the distinction between \emph{meaning theory} and \emph{model theory}.
}
